Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-29 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:28	16:32:50	(Mon28.Sep)
la2pdf commit - 2015:09:28	18:41:30	(Mon28.Sep)
la2pdf commit - 2015:09:29	16:07:54	(Tue29.Sep)

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{\emph{Determining Kaiser parameter boundaries}: LCA images created with a large and equal size window database, but where the upper bounds for $\beta$ and $\phi$ is varied. The upper left image is equal to DAS with a rectangular window. For all images we measure the lateral distance $\Delta x$ between the two -3dB points of the anchor. These are specified relatively to the reference distance  $\Delta x_\text{ref}$ from the upper left DAS image.
\newline
\emph{Upper bound $\beta$:}\hfill
\parbox[t]{.89\linewidth}{Observe that LCA gets better at suppressing sidelobes in the image as we increase the upper bounds for $\beta$. \Fig{mvdr_selected_windows} suggests that MVDR tend to choose windows with levels lower than that of Kaiser with $\beta=2$, but here we observe further improvement going to $\beta=5$.}\newline
\emph{Upper bound $\phi$:}\hfill
\parbox[t]{.89\linewidth}{As we increase the upper bound of the steering $\phi$, we also increase the lateral image resolution. }
}\label{oversampling_mosaic_bounds}
\end{figure*}

@@

\begin{figure*}[t]\centering
\subfloat[]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_holmengraa.pdf}%%
\label{oversampling_mosaic_bounds_beta}}
\hfil
\subfloat[]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_cross.pdf}%
\label{oversampling_mosaic_bounds_phi}}
\caption{}\label{fig_sim}
\end{figure*}

@@

@@

@@

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with with responses similar to the ones MVDR computes. We study this in \Fig{mvdr_selected_windows}, where the typical responses MVDR creates for shadow, speckle and highlight regions in the Holmengraa scene is presented.

Observe from \Fig{mvdr_selected_windows} that MVDR seems prefers symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated sector of the seafloor. We have observed this symmetry to be a side-effect of the averaging steps needed to build the sample covariance matrix, which is key to allow  MVDR to run in near snapshot mode in an active system. The peak sidelobe levels of the MVDR windows they are mostly between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively.

@@

TODO. Add image of DAS vs. MVDR vs. LCA Kaiser vs. LCA Trig

>>>>

\begin{figure*}[t]%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{\emph{Determining Kaiser parameter boundaries}: LCA images created with a large and equal size window database, but where the upper bounds for $\beta$ and $\phi$ is varied. The upper left image is equal to DAS with a rectangular window. For all images we measure the lateral distance $\Delta x$ between the two -3dB points of the anchor. These are specified relatively to the reference distance  $\Delta x_\text{ref}$ from the upper left DAS image.
\newline
\emph{Upper bound $\beta$:}\hfill
\parbox[t]{.89\linewidth}{Observe that LCA gets better at suppressing sidelobes in the image as we increase the upper bounds for $\beta$. \Fig{mvdr_selected_windows} suggests that MVDR tend to choose windows with levels lower than that of Kaiser with $\beta=2$, but here we observe further improvement going to $\beta=5$.}\newline
\emph{Upper bound $\phi$:}\hfill
\parbox[t]{.89\linewidth}{As we increase the upper bound of the steering $\phi$, we also increase the lateral image resolution. }
}\label{oversampling_mosaic_bounds}
\end{figure*}

@@

\begin{figure*}[t]\centering
\subfloat[LCA using Kaiser windows, LCA using trigonometric windows, and MVDR. Two lateral image cuts are shown in the leftmost figures, along with the response of a rectangularly weighted DAS. Note how the FWHM of LCA sits in between that of DAS and MVDR. Also note how LCA is insensitive to the window type; its performance is near identical whether it uses Kasier or trigonometric windows.]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_cross.pdf}%
\label{beamformer_comparison_cross}}
\hfil
\subfloat[Image of Holmengraa. All the adaptive beamformers offer improvement compared to DAS. The shadows are deeper, the edges better refined and the detail level is higher.]{\includegraphics[width=\textwidth]{gfx/beamformer_comparison_holmengraa.pdf}%%
\label{beamformer_comparison_holmengraa}}
\caption{Image quality: Comparing DAS with MVDR and LCA with Kaiser and trigonometric windows.}\label{image_quality}
\end{figure*}

@@

% \begin{figure*}[t]%\centering%
% \includegraphics[width=\textwidth]{gfx/beamformer_comparison_cross.pdf}%
% \caption{}\label{beamformer_comparison_cross}
% \end{figure*}
% 
% \begin{figure*}[t]%\centering%
% \includegraphics[width=\textwidth]{gfx/beamformer_comparison_holmengraa.pdf}%
% \caption{}\label{beamformer_comparison_holmengraa}
% \end{figure*}

@@

\subsection{Using trigonometric windows instead of Kaiser}

\begin{align}
\phi_\text{3dB}(\beta) \approx \minus{}2.214\beta^3 + 6.084\beta^2 - 5.710\beta + 2.136
\end{align}

@@

Assuming that a robust MVDR is the reference method we want LCA to perform similarly to, it seems sensible to create window database for LCA with with responses similar to the ones MVDR computes. We study this in \Fig{mvdr_selected_windows}, where we present the typical responses that MVDR creates for shadow, speckle and highlight regions of the Holmengraa scene.

Observe from \Fig{mvdr_selected_windows} that MVDR seems to prefer symmetric window responses, even if it is free to choose non-symmetric ones. The symmetry is most predominant in shadow and speckle regions, while in highlight the windows are approximately symmetric within the illuminated sector of the seafloor. We have observed this symmetry to be a side-effect of the averaging steps needed to build the sample covariance matrix, which is required to allow MVDR to run in near snapshot mode in an active system. The peak sidelobe levels of the MVDR windows are mostly between -13\,dB and -43\,dB. This corresponds to that of the rectangular and Hamming window, or a Kaiser window with $\beta=0$ and $\beta=2$, respectively.

@@

We compare LCA image quality to that of DAS and MVDR in \Fig{image_quality}. \Fig{beamformer_comparison_cross} are of the cross, were we display the images computed by LCA using Kaiser windows, LCA using trigonometric windows, and MVDR.

 \Fig{beamformer_comparison_holmengraa}
